\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-05 coqimpl.tex
Update propositional partial recursor Update intro with structure and contribution.

We emphasize that in \cref{thm:prec-complete}, each function $"d"_i$ can
actually be considered as a constructor, because they can be reflected
to real constructors of "C" using the left inverse "linv" (directly generalization of "reflect : self_B.b → option bool" of the above). Thus, \cref{thm:prec-complete}
implies that (1) every future extension of the inductive type can
support this partial recursion (trivially); (2) every type supporting
this partial recursor with its computational axioms at least supports
these constructors because of the embedding. In other words, \textit{a
type (at least) supports these constructors if and only if this type
supports the corresponding partial recursor (with the computational
axioms)}.  Thus, we can argue that the partial recursor gives a sound and
complete extensional characterization of all the extension of a given (non-indexed)
inductive type.\YZ{What about indexed inductive types?}

We can support partial dependent eliminator as well, but partial dependent eliminator can deduce "prec" and our "prec" is enough to contruct this left inverse for (non-indexed) inductive type. 
\begin{minted}{Coq}
  pdelim : ∀ (P : D -> Set), .., 
  (rᵢ : (∀ (x : Aᵢ) (w : Bᵢ x -> D), (∀ (b : Bᵢ x), option (P (w b))) 
    -> option (P (dᵢ x w)))),  .., ∀ (d : D) -> option (P d)
\end{minted}
% To generalize to indexed inductive type, we base on indexed W type~\cite{martin1982constructive, morris2009indexed,jashug2017}. Please refer to

>>>>

We emphasize that in \cref{thm:prec-complete}, each function $"d"_i$ can
actually be considered as a constructor, because they can be reflected
to real constructors of "C" using the left inverse "linv" (directly generalization of "reflect : self_B.b → option bool" of the above). Thus, \cref{thm:prec-complete}
implies that (1) every future extension of the inductive type can
support this partial recursion (trivially); (2) every type supporting
this partial recursor with its computational axioms at least supports
these constructors because of the embedding. In other words, \textit{a
type (at least) supports these constructors if and only if this type
supports the corresponding partial recursor (with the computational
axioms)}.  Thus, we can argue that the partial recursor gives a sound and
complete extensional characterization of all the extension of a given (non-indexed)
inductive type.\YZ{What about indexed inductive types?}\EDJreply{Done. I also have a formalization of this proof now, for indexed type and dependent eliminator. Though the formalization is about single constructor.}

We can support partial dependent eliminator as well, but partial dependent eliminator can deduce "prec" and our "prec" is enough to contruct this left inverse for (non-indexed) inductive type. 
\begin{minted}{Coq}
  pdelim : ∀ (P : D -> Set), .., 
  (rᵢ : (∀ (x : Aᵢ) (w : Bᵢ x -> D), (∀ (b : Bᵢ x), option (P (w b))) 
    -> option (P (dᵢ x w)))),  .., ∀ (d : D) -> option (P d)
\end{minted}
To generalize to indexed inductive type, we need to base on indexed W type~\cite{martin1982constructive, morris2009indexed,jashug2017} and dependent eliminator is unavoidable. Please refer to the supplementary material and appendix for a formalization of the left inverse in the context of indexed inductive type.

### 2022-07-05 introduction.tex
Update propositional partial recursor Update intro with structure and contribution.

>>>>

\large{\textbf{Structure of the paper}} We will quickly introduce Family Polymorphism and the challenges to adapt it into dependent type setting in \cref{sec:background+challenge}. After that, we will talk about the language design of family polymorphism in dependent type setting and the implementation of our Coq plugin in \cref{sec:coqimpl}. Then, we consider the meta-theory of incorporating family polymorphism into predicative MLTT, and deriving consistency and canonicity results in \cref{sec:metatheory}. \ref{sec:related-work} discusses related works and \ref{sec:conclusion} concludes.

\large{\textbf{Contributions}} include the following
\begin{itemize}
  \item To our knowledge, this is the first attempt incorporating family polymorphism with theorem proving and higher order logic
  \item We contribute a prototypical Coq plugin for the interested users and developers 
  \item We provide some first-step meta-theoretical results, including consistency and canonicity
\end{itemize}
